TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-14 paper/draft.tex
hogg note
training description

\subsection{\apogee\ Survey}
% \begin{enumerate}
% Describe the \apogee\ data (survey mission: \citealt{Majewski:2015}; target selection: \citealt{Zasowski:2013}; ASPCAP pipeline: \citealt{Perez:2016}).

% \item[-] Some M dwarfs in \apogee\ proposed as ancilliary targets (Blake/Covey sources), plus an unknown number observed unintentionally \citep{Desphande:2013}.
% \end{enumerate}

@@

\thecannon\ model can in principle be trained on any physical or empirical labels available. However, limitations to consider are that test labels from \thecannon\ are only accurate if the training labels accurate, and only precise if the training labels are measured using a consistent method. \thecannon\ does not extrapolate well outside the parameter space of the training sample.

Inferring the label of a star with such a model requires two steps: first the \emph{training step} in which a generative model is constructed at each pixel from the set of reference labels and fluxes, and second the \emph{test step} in which the model is applied to determine the labels of a spectrum.

@@

JB: The training step description: OPTIMIZE THETA AT FIXED LABELS.

JB: Test step description: OPTIMIZE LABELS AT FIXED THETA.

>>>>

\subsection{\apogee\ Survey}

@@

\thecannon\ model can in principle be trained on any physical or empirical labels available. However, limitations to consider are that test labels from \thecannon\ are only accurate if the training labels accurate, and only precise if the training labels are measured using a consistent method. \thecannon\ does not extrapolate well outside the parameter space of the training sample.
\color{gcolor}{HOGG: More notes to add here?}\color{black}

Inferring the label of a star with such a model requires two steps: first the \emph{training step} in which a generative model describing the probability density function (pdf) of the flux is constructed at each pixel from the set of spectrum with known reference labels, and second the \emph{test step} in which the model is applied to determine the labels of a spectrum.

@@

% JB: The training step description: OPTIMIZE THETA AT FIXED LABELS.
% JB: Test step description: OPTIMIZE LABELS AT FIXED THETA.
